Tidal field anisotropy as a tracer of cosmic voids

### 2015-01-15 cosmic_voids.tex
Introduction to Properties of voids

Since voids were found in the first compiled galaxy surveys 
they have been identified as one of the most striking features of the
Cosmic Web \citep{Chincarini75,  Gregory78, Einasto80M, Einasto80N,
  Kirshner81, Zeldovich82,Kirshner87, Bond96}. 
However,  due to the large volume extension of void regions ($\sim
5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogs of
voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
through  modern galaxy surveys like the two-degree field Galaxy
Redshift Survey \citep{ Colless01, Colless03} and the Sloan Digital
Sky Survey \citep{York00, Abazajian03}.
This advancement generated a great interest to study voids
observationally during the last decade \citep{Hoyle04, Croton04, Rojas05,
  Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
  BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}.

@@

As suggested by \citet{Platen07} and references therein, it is necessary to
apply a threshold merger in order to reduce spurious features and to avoid 
void hierarchization. A natural choice is a threshold of $\delta = -0.8$, 
which means that any ridge between two voids with density below that value
would be removed and the respective voids merged. As we are working with the
FA, the equivalent threshold according to Fig. \ref{fig:L1_correlations} is
$FA = 0.65$. In right panels of Fig. \ref{fig:FA_field} we show the resulting
catalogs of voids for both schemes.

@@

  \captionof{figure}{\small Volume size distribution of voids for both
  catalogs. FA-Tweb (red curves), FA-Vweb (blue curves).
  Continuous lines corresponds with the total number of voids, dot-dashed
  with sub-compensated voids and dashed lines with over-compensated voids. }

@@

%-------------------------------------------------------------------------
\subsection{Physical profiles of voids}
\label{subsec:density_voids}
%-------------------------------------------------------------------------

@@

  \captionof{figure}{\small Density of voids for each finding scheme.}

@@

>>>>

Since voids were found in the first compiled galaxy surveys 
they have been identified as one of the most striking features of the
Cosmic Web \citep{Chincarini75,  Gregory78, Einasto80M, Einasto80N,
  Kirshner81, Zeldovich82,Kirshner87, Bond96}. 
However,  due to the large volume extension of void regions ($\sim
5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogues of
voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
through  modern galaxy surveys like the two-degree field Galaxy
Redshift Survey \citep{ Colless01, Colless03} and the Sloan Digital
Sky Survey \citep{York00, Abazajian03}.
This advancement generated a great interest to study voids
observationally during the last decade \citep{Hoyle04, Croton04, Rojas05,
  Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
  BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}.

@@

As suggested by \citet{Platen07} and references therein, it is necessary to
apply a threshold merger in order to reduce spurious features and to avoid 
void hierarchization. A natural choice is a threshold of $\delta = -0.8$, 
which means that any ridge between two voids with density below that value
would be removed and the respective voids merged. As we are working with the
FA, the equivalent threshold according to Fig. \ref{fig:L1_correlations} is
$FA = 0.65$. In right panels of Fig. \ref{fig:FA_field} we show the resulting
catalogues of voids for both schemes.

@@

  \captionof{figure}{\small Volume size distribution of voids for both
  catalogues. FA-Tweb (red curves), FA-Vweb (blue curves).
  Continuous lines corresponds with the total number of voids, dot-dashed
  with sub-compensated voids and dashed lines with over-compensated voids. }

@@

%-------------------------------------------------------------------------
\subsection{Physical profiles of voids}
\label{subsec:properties_voids}
%-------------------------------------------------------------------------

@@

  \captionof{figure}{\small Physical internal properties of voids for 
  the two finding scheme. Density field (left panels), radial-projected
  velocity field (middle panels) and FA field (right panels). The analysis
  is performed for both, subcompensated (first two rows) and overcompensated
  voids (last two rows).}

@@

In Fig. \ref{fig:RhoVel} we analyse the internal properties of the found 
voids. We calculate the contrast density, radial-projected velocity and 
FA profiles. For this purpose we catalogue all the voids into several 
radial bins in order to capture possible size effects. Then, for each void, 
we take the distance of each member cell to the void centre along with the 
properties of interest. Normalizing these distances with the effective 
radius, we stack all the voids catalogued in a radial bin in order to 
compute radial profiles of the properties of interest.

%.........................................................................
\subsubsection{Density profiles}
\label{subsubsec:density_voids}
%.........................................................................

In Fig. \ref{fig:RhoVel} we analyse the internal properties of the found 
voids. We calculate the contrast density, radial-projected velocity and 
FA profiles. For this purpose we catalogue all the voids into several 
radial bins in order to capture possible size effects. Then, for each void, 
we take the distance of each member cell to the void centre along with the 
properties of interest. Normalizing these distances with the effective 
radius, we stack all the voids catalogued in a radial bin in order to 
compute radial profiles of the properties of interest.

%.........................................................................
\subsubsection{Velocity profiles}
\label{subsubsec:velocity_voids}
%.........................................................................

%.........................................................................
\subsubsection{FA profiles}
\label{subsubsec:FA_voids}
%.........................................................................
